---
title: "Methods Appendix"
bibliography: [references.bib]
output: 
  bookdown::pdf_document2:
    template: appendix_template.tex
    keep_tex: true
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
                      message = FALSE, warning = FALSE)

```


```{r libs, include = FALSE}

library(knitr)
library(rmarkdown)
library(tidyverse)
library(stargazer)
library(sjPlot)
library(sessioninfo)
library(kableExtra)
library(reshape)

```

First, I've included code to display your current $\textsf{R}$ session information. All of the information will end up in the object `si` in your current session's environment. You can call them one-at-a-time in the text if you like. 

```{r sesh, include = TRUE, results = 'asis'}

si <- session_info()
sip.dat <- si$platform %>%
  melt()

sip.dat <- sip.dat[,c("L1", "value")]
sip.dat$value <- gsub("@.*","", sip.dat$value)

kable(sip.dat, col.names = NULL, caption = "Session Information: Platform") %>%
  kable_styling(full_width = F)

```

You might decide that you want to say that you are running `r si$platform$version` in `r si$platform$ui` `r si$platform$rstudio` on a MacBook Pro `r si$platform$system` running `r si$platform$os`. Alternatively, you might wish to display all of the information in a table of some sort. I've done this in Table \@ref(tab:sesh).

You'll probably want to organize your methods appendix using subheadings (with two # signs) or sub-subheadings (with three # signs). You'll be able to use numbered equations, figures, tables, etc.